---
title: "Assignment: R Markdown Part 2"
date: "4/13/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_print: paged
    theme: cerulean
---

# Plants {.tabset}

This assignment is perfomed using Plant Growth dataset.

```{r include=FALSE}
?rmarkdown::html_document
```

## Shrubs

Shrubs are perennial woody plants, and therefore have persistent woody stems above ground (compare with herbaceous plants).Usually shrubs are distinguished from trees by their height and multiple stems.

## Herbs

Herbs are plants with savory or aromatic properties that are used for flavoring and garnishing food, for medicinal purposes, or for fragrances; excluding vegetables and other plants consumed for macronutrients.

# Plant growth data points and box-plot

```{r echo=FALSE, fig.show='hold', message=FALSE, warning=FALSE, out.width="50%"}

library(tidyverse)

plot <- ggplot(PlantGrowth, aes(x=weight, y=group))+ geom_point()

#left image
plot

#right image
plot + geom_boxplot()
```

# Ozone layer data
Predict the daily maximum one-hour-average ozone reading (V4).

## Ozone Layer data

```{r}
data("Ozone", package = "mlbench")
# remove missing values and create temporary dataframe
Ozo <- na.omit(Ozone)
Ozo
```

# Life plantation maths
Let's assume an individual plants one tree each 3 months and grows it.
Average human tree planting life can be considered 35 years.

```{r}
A <- 35
B <- A*(12/4)
B
```

<span style="color:green;">
An individual can potentially plant `r B` trees in a life time.
</span>

# Plant Growth
library(htmlwidgets)

## Weight data group Wise

```{r  message=FALSE, warning=FALSE}
library(DT)
data("PlantGrowth", package='ggplot2')
datatable(head(PlantGrowth, 100),
          rownames=TRUE, 
          extensions='Scroller', filter='top',
          options = list(dom = "tiS", scrollX=TRUE,
                         scrollY = 400,
                         scrollCollapse = TRUE)
          )
```
